---
title: "Homework 5"
author: "Mayuri Albal"
date: "2022-11-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(rvest)
library(ggplot2)
```

```{r}
twp_data = read_csv(file= "./data/homicide-data.csv") %>%
janitor::clean_names()
```

**Describe the Raw Data**
Within the original data set there are 52,719 observations and 12 variables. The variables names include: 'uid', 'reported_date', 'victim_last', 'victim_first', 'victim_race', 'victim_age', 'victim_sex', 'city', 'state', 'lat', 'lon', and 'disposition'. This data was collected across different police department reports from 50 of the largest cities in the United States from the past decade.

City and State Variable Made
```{r}
murder_df=
twp_data %>%
janitor::clean_names() %>% 
mutate(
  state= replace(state, state == "AL", "OK"),
  state = replace(state, state== "wI", "WI")
) %>% 
mutate(
  city_state= paste(city, state, sep= ","))


```

Solved and Unsolved Case Count
```{r}
case_count= 
murder_df %>% 
  group_by(city_state) %>% 
  summarize(unsolved_n = sum(disposition== 'Closed without arrest',
                             disposition == 'Open/No arrest'),
                          total_m= n()) 
```

Prop.Test for Baltimore
```{r}
baltimore.test=
  case_count %>% 
  filter(city_state == "Baltimore,MD") %>% 
  transform(
    prop = map2(unsolved_n, total_m, ~prop.test(.x, .y) %>% 
      broom::tidy())) %>% 
    unnest() %>% 
  select(prop.estimate, prop.conf.low, prop.conf.high)
```

Prop.test All Cities
```{r}
all_cities = 
case_count %>% 
  mutate(
    prop= map2(unsolved_n, total_m, ~prop.test(.x, .y) %>% 
      broom::tidy())) %>% 
    unnest() %>% 
  select(city_state, estimate, conf.low, conf.high)

all_cities_output=
  all_cities %>% 
  knitr::kable() 
  
```

Plotting

```{r}
ggplot(all_cities, aes(x= reorder(city_state,estimate), y= estimate, color=city_state))+
  geom_point()+
  geom_errorbar(aes(ymin=conf.low, ymax= conf.high))+
  theme_classic()+ 
  theme(legend.position= "none")+
  ggtitle("Proportion Estimated of Unsolved Homicide in Large US Cities")+
  theme(plot.title = element_text(hjust= 0.5),
        axis.text.x.bottom = element_text(size= 7, angle= 90))+
    labs(x = "City",
        y= "Estimate of Proportion")
  
```

