---
title: "Homework 5"
author: "Mayuri Albal"
date: "2022-11-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(rvest)
```

```{r}
twp_data = read_csv(file= "./data/homicide-data.csv") %>%
janitor::clean_names()
```

**Describe the Raw Data**
Within the original data set there are 52,719 observations and 12 variables. The variables names include: 'uid', 'reported_date', 'victim_last', 'victim_first', 'victim_race', 'victim_age', 'victim_sex', 'city', 'state', 'lat', 'lon', and 'disposition'. This data was collected across different police department reports from 50 of the largest cities in the United States from the past decade.

City and State Variable Made
```{r}
murder_df=
twp_data %>%
janitor::clean_names() %>% 
mutate(
  city_state= paste(city, state, sep= ",") %>% 
  group_by(city_state) %>% 
  summarize(unsolved_n = sum(disposition == 'Closed without Arrest',
                             disposition == 'Open/No Arrest'),
    total_m= n()) 

```

Solved and Unsolved Case Count
```{r}
murder_df %>% 
  group_by(city_state) %>% 
  summarize(unsolved_n = sum(disposition== 'Closed without arrest',
                             disposition == 'Open/No arrest'),
                          total_m= n()) 
```

Prop.Test

```{r}
baltimore.test=
  murder_df %>% 
  
```

